---
name: Galen Holt
# surname: Holt
position: "Research Fellow"
# pronouns: he/him # this worked on my website repo
address: "Centre for Regional and Rural Futures, Deakin University"
phone: +61 4 8859 2586
www: galenholt.github.io
email: "g.holt@deakin.edu.au"
github: galenholt
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000000"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Research interests

-   Freshwater community ecology at multiple spatial and temporal scales
-   Community response to environmental change
-   Aquatic species conservation and management
-   Multiscale ecological processes
-   Species coexistence and biodiversity maintenance
-   Spatial and temporal environmental variation
-   Dispersal
-   Trophic dynamics

# Positions

```{r}
tribble(
  ~startdate, ~enddate, ~Title, ~Organisation,
  2021, "Present", "Research Fellow", "Deakin University Centre for Regional And Rural Futures",
  2020, "Present", "Visiting Scientist", "CSIRO",
  2018, "2020", "Associate Research Fellow", "Deakin University CeRRF",
  2015, "2018", "Postdoctoral Scholar", "University of Arizona Ecology and Evolutionary Biology",
  2017, "2018", "Postdoctoral Scholar", "University of Wisconsin Center for Limnology"
) %>%
  detailed_entries(
    when = glue::glue("{as.character(startdate)} -- {as.character(enddate)}"),
    what = glue::glue("{Title} - {Organisation}")
  )
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution,
  "PhD", "2014", "University of Arizona",
  "BA, Honors", "2004", "Williams College") %>%
  detailed_entries(Degree, Year, Institution)
```

# Publications

## In prep and review

```{r}
# library(dplyr)
# knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("CV/In prepreview.bib")
```

## Peer-reviewed publications

```{r}
bibliography_entries("CV/My papers.bib") %>%
  arrange(desc(author$family), issued)
```

## Non-peer-reviewed publications

```{r}
bibliography_entries("CV/My reports.bib") %>%
  arrange(desc(author$family), issued)
```
